### 2025-09-15 paper/fig/scigen-1805.02474v1-10-src.tex
Better helper functions.

\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid,mathescape=false]{../website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Source code for \figref{scigen-example-website}}
    \label{fig:fluid-example-paragraph}
\end{figure}

>>>>

\begin{figure}[h]
    \small
    \begin{lstlisting}[language=Fluid,mathescape=false]
let model_ name = model name tableData in """
As shown in Table 3, BiLSTM gives significantly ${trendWord (model_ "BiLSTM").acc (model_ "LSTM").acc
betterWorse} accuracies compared to uni-directional LSTM2, with the training time per epoch ${trendWord (model_
"BiLSTM").time_s (model_ "LSTM").time_s growShrink} from ${numToStr (model_ "LSTM").time_s} seconds to ${numToStr
(model_ "BiLSTM").time_s} seconds. Stacking 2 layers of BiLSTM gives ${trendWord (model_ "2 stacked BiLSTM").acc
(model_ "BiLSTM").acc improve} to development results, with a ${trendWord (model_ "2 stacked BiLSTM").time_s
(model_ "BiLSTM").time_s smallerHigher} time of ${numToStr (model_ "2 stacked BiLSTM").time_s} seconds. 3 layers
of stacked BiLSTM ${trendWord (model_ "3 stacked BiLSTM").acc (model_ "BiLSTM").acc improve} the results. In
contrast, S-LSTM gives a development result of ${numToStr (model_ "S-LSTM").acc} %, which is significantly
${trendWord (model_ "S-LSTM").acc (model_ "2 stacked BiLSTM").acc betterWorse} compared to 2-layer stacked
BiLSTM, with a ${trendWord (model_ "S-LSTM").param (model_ "2 stacked BiLSTM").param smallerHigher} number of
model parameters and a ${trendWord (model_ "S-LSTM").time_s (model_ "2 stacked BiLSTM").time_s shorterLonger}
time of ${numToStr (model_ "S-LSTM").time_s} seconds.  We additionally make comparisons with stacked CNNs and
hierarchical attention (Vaswani et al., 2017), shown in Table 3 (the CNN and Transformer rows), ${(findWithKey'
"time_s" (minimum (map (fun y -> y.time_s) tableData)) tableData).model} is the ${rankLabel "most efficient"
(findIndex "model" "CNN" (insertionSort (fun a b -> a.time_s < b.time_s) tableData))} among all models compared,
with the ${rankLabel "smallest" (findIndex "model" "CNN" (insertionSort (fun a b -> a.param < b.param) tableData)
)} model size. On the other hand, a 3-layer stacked CNN gives an accuracy of ${numToStr (model "3 stacked CNN"
tableData).acc} %, which is also the ${rankLabel "lowest" (findIndex "model" "CNN" (insertionSort (fun a b ->
a.time_s < b.time_s) tableData))} compared with BiLSTM, hierarchical attention and S-LSTM. The ${rankLabel "best"
(findIndex "model" "S-LSTM+Attention" (insertionSort (fun a b -> b.acc < a.acc) tableData))} performance of
hierarchical attention is obtained by S-LSTM+Attention in terms of both accuracy and efficiency. S-LSTM gives
significantly ${trendWord (model_ "S-LSTM").acc (model_ "CNN").acc betterWorse} accuracies compared with both CNN
and hierarchical attention. Table 3 additionally shows the results of BiLSTM and S-LSTM when external attention
is used. Attention leads to improved accuracies for both BiLSTM and S-LSTM in classification, with S-LSTM still
${trendWord (model_ "S-LSTM").acc (model_ "BiLSTM").acc underOverPerforming} BiLSTM significantly."""
    \end{lstlisting}
    \caption{Source code for \figref{scigen-example-website}}
    \label{fig:fluid-example-paragraph}
\end{figure}

### 2025-09-15 paper/sec/introduction.tex
Extract figure.
Import source directly into figure.
Better helper functions.

Recent work on data provenance and data visualisation~\citep{psallidas18smoke,perera22,bond25} integrating
interactive provenance queries into charts and figures using \emph{transparent programming languages} which
track data provenance automatically as data flows through a computation. Visual outputs produced using these
platforms allow readers to interact with visual elements to see the relevant data. In most article charts and
figures usually only play a supporting role, however. The main claims are usually presented in natural
language which also makes quantitative claims and refers to data analyses which are not present in the final
artifact.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{fig/scigen-1805.02474v1-10-with-pointer.png}
    \caption{Transparent Text with Interactive Provenance Queries}\label{fig:scigen-example-website}
\end{figure}

>>>>

Recent work on data provenance and data visualisation~\citep{psallidas18smoke,perera22,bond25} integrating
interactive provenance queries into charts and figures using \emph{transparent programming languages} which
track data provenance automatically as data flows through a computation. Visual outputs produced using these
platforms allow readers to interact with visual elements to see the relevant data. In most article charts and
figures usually only play a supporting role, however, with the main claims usually presented in natural
language. This language makes quantitative claims and refers to ``behind the scenes'' data analyses.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{fig/scigen-1805.02474v1-10-with-pointer.png}
    \caption{\emph{Transparent text} links fragments of natural language to underlying data, via queries}\label{fig:scigen-example-website}
\end{figure}

\input{fig/scigen-1805.02474v1-10-src}
